---
title: "Analysis of merged questionnaires"
author: "Anna Quaglieri & Riccardo Amorati"
date: "03/09/2017"
output:
  github_document:
    toc: yes
    toc_depth: 4
  html_document:
    toc: yes
    toc_depth: '4'
  html_notebook:
    code_folding: hide
    fig_caption: yes
    number_sections: yes
    toc: yes
    toc_float: yes
---

# Plan that I wrote with Richi's comments

Link at https://docs.google.com/document/d/1bdNeOMAYY90k8FAbPRWGBgS1YBEdP09kP0vcW0tNgPc/edit?usp=sharing


```{r,message=FALSE, echo=FALSE}
library(readr)
library(tidyverse)
library(reshape2)
library(corrplot)
library(psych)
library(pheatmap)
library(RColorBrewer)
library(cowplot)
library(gridExtra)
library(cowplot)
library(pheatmap)
library(sjPlot)
library(sjlabelled)
library(sjmisc)
library(knitr)

data(efc)
theme_set(theme_sjplot())

# Chunk options
knitr::opts_chunk$set(echo = TRUE, prompt = TRUE,cache = TRUE,fig.width = 12,fig.height = 12)

```

# Read in data

```{r message=FALSE,message=FALSE}
european <- read_csv("01-cleaning_data_data/european_recoded.csv")
australian <- read_csv("01-cleaning_data_data/australian_recoded.csv")

dim(european)
dim(australian)

european$EU <- 1
australian$AU <- 1

all <- merge(european,australian,all = TRUE)

table(all$EU,all$AU,useNA = "always")
```

## Variables to describe dataset (can be different between contexts)

```{r}
demographics_var <- c("Age","Gender","L1","speak.other.L2","study.other.L2","origins","year.studyL2","other5.other.ways","degree","roleL2.degree","study.year","prof","L2.VCE","uni1.year","Context")
l2School <- "\\.L2school$"
l2School_variables <- colnames(all)[grep(l2School,colnames(all))]
```

- First language

```{r}
#table(all$L1,all$Context) # too many levels - needs to be cleaned (ex tot number of languages?)
table(all$L1,useNA = "always")
ggplot(all,aes(x=L1,fill=Context)) + geom_bar() + coord_flip() + ggtitle("First Language") + labs(y="N. of participants",x="")+theme_bw()
#table(all$speak.other.L2,all$Context)
```

```{r}
L2 <- data.frame(Freq=table(all$speak.other.L2)[order(table(all$speak.other.L2),decreasing = TRUE)],
                 L2=names(table(all$speak.other.L2))[order(table(all$speak.other.L2),decreasing = TRUE)]) # too many levels - needs to be cleaned (ex tot number of languages?)
head(L2)
```

- origins

```{r}
table(all$origins,useNA = "always")
```


```{r}
table(all$year.studyL2)
```

```{r}
table(all$degree)
```

- study.year in the European context is uni1.year in the Australian context

```{r}
all$study.year[is.na(all$study.year)] <- all$uni1.year[is.na(all$study.year)]
#table(all$study.year)
all$study.year <- ifelse(all$study.year == "Already graduated after 5 semesters in March 2016, was interested in survery/study, sorry.","6th semester",all$study.year)
table(all$study.year)
```

- proficiency

```{r}
table(all$prof,useNA = "always")
```

# Filter participants : keep only the ones that meet the inclusion criteria

```{r Filtered,fig.width=20,fig.height=15}
all$study.year[is.na(all$study.year)] <- all$uni1.year[is.na(all$study.year)]
# Filter only subject that we want to include in the study
# names(table(all$study.year))[1] = 1st semester"

filtered <- subset(all, (study.year == "1st year") | (study.year == names(table(all$study.year))[1]) & year.studyL2 != "0 years")

table(filtered$Context)
table(all$Context)
```

# Define demographic variables

## Need to check datasets with Rcihi (why do we have QC in L1? Am I using not the latest dataset?)

```{r message=FALSE}
all <- filtered
demographics_var <- c("Age","Gender","L1","speak.other.L2","study.other.L2","origins","year.studyL2","other5.other.ways","degree","roleL2.degree","study.year","prof","L2.VCE","uni1.year","Context")
l2School <- "\\.L2school$"
l2School_variables <- colnames(all)[grep(l2School,colnames(all))]

ggplot(all,aes(x=L1,fill=Context)) + geom_bar() + coord_flip() + ggtitle("First Language") + labs(y="N. of participants",x="") + theme_bw()

table(all$L1,all$Context)

table(all$degree,all$L1)
```

- Check for L1 but we decided not to filter for it

```{r}
#Filter by L1

nc <- names(table(all$Context))
table(all$Context)
l1_filter <- all[(all$Context == nc[1] & (all$L1 == "German" | all$L1 == "German and English")) | 
                    (all$Context == nc[2] & (all$L1 == "Italian")) | 
                    (all$Context == nc[3] & (all$L1 == "English" | all$L1 == "English and Dutch" | all$L1 == "German and English")) |
                    (all$Context == nc[4] & (all$L1 == "English" | all$L1 == "English and Dutch" | all$L1 == "German and English")),]


#all <- l1_filter

# do not filter for L1
all <- all

# subset demographics
demo <- subset(all,select=c("Resp.ID",demographics_var,l2School_variables))

# Numeri finali
table(l1_filter$Context)
table(all$Context)

```

- Filter missing value:
  - Filter participants who didn't put the degree
  - we don't care about speak.other.L2 and study.other.L2

```{r}
missing_bySample <- rowSums(is.na(demo))
names(missing_bySample) <- demo$Resp.ID
missing_byVar <- colSums(is.na(demo))
names(missing_byVar) <- colnames(demo)

barplot(missing_bySample)
d <- data.frame(miss=missing_byVar)
d$varID <- rownames(d)
ggplot(data=d,aes(x=varID,y=miss)) + geom_bar(stat="identity") + theme_bw() +theme(axis.text.x = element_text(angle = 45, hjust = 1)) 


demo_missing <- demo %>% group_by(Context) %>% summarise(roleL2.degree_na = sum(is.na(roleL2.degree)),
                                                         L2.VCE_na = sum(is.na(L2.VCE)),
                                                         other5.other.ways_na=sum(is.na(other5.other.ways )),
                                                         uni1.year_na = sum(is.na(uni1.year)),
                                                         primary1.L2school_na=sum(is.na(primary1.L2school)),
                                                         CLS3.L2school_na = sum(is.na(CLS3.L2school)),
                                                         VSL4.L2school_na=sum(is.na(VSL4.L2school)),
                                                         degree = sum(is.na(degree)),
                                                         schooL2country5.L2school_na=sum(is.na(schooL2country5.L2school)))

# We do not filter for speak.other.L2 or study.other.L2

#demo[is.na(demo$speak.other.L2),]
# teniamo
#demo[is.na(demo$study.other.L2),]
missing_bySample[names(missing_bySample) == "5166861581"]
#demo[is.na(demo$year.studyL2),]
missing_bySample[names(missing_bySample) == "5378798787"]

# remove NA from degree
#table(demo$degree,useNA = "always")
# Remove people
all <- all[!is.na(all$degree),]


table(all$Context)
```

## Write filtered and merged dataset

```{r}
write.csv(all,file.path("02-descriptive_data/context-merged_filtered.csv"))
```

## Descriptive plots and tables

- Summary demographics TO DO: - to change yearL2.study.richi 

```{r age_by_context,message=FALSE}
# add numbers on the bar

# tabAge <- t(table(all$Age,all$Context))
# ggplot(all,aes(x=Age,fill=Context)) + geom_bar(position="dodge",colour="white")   + labs(y="N participants") + scale_y_continuous(breaks=seq(0,90,10),limits=c(0,90)) + theme_bw() + draw_grob(tableGrob(tabAge), x=2.5, y=40, width=0.3, height=0.4) + ggtitle("Participants by age")
# tabAge

tabAge <- t(table(all$Age,all$Context))
ggdf <- data.frame(Age = rep(colnames(tabAge),each=4)[!(as.numeric(tabAge) == 0)],
  N.Participants = as.numeric(tabAge)[!(as.numeric(tabAge) == 0)],
  Context = rep(rownames(tabAge),times=3)[!(as.numeric(tabAge) == 0)])

ggplot(ggdf,aes(x=Age,y=N.Participants,fill=Context)) + geom_bar(position="dodge",colour="white",stat="identity")  + scale_y_continuous(breaks=seq(0,90,10),limits=c(0,90)) + theme_bw() + ggtitle("Participants by age")+
  geom_text(aes(label = N.Participants), hjust=0.5, vjust=-0.25, size = 2.5,position=position_dodge(width=0.9)) 

```

```{r gender_by_context,message=FALSE}
# add numbers on the bar

tabAge <- t(table(all$Gender,all$Context))
ggdf <- data.frame(Gender = rep(colnames(tabAge),each=4)[!(as.numeric(tabAge) == 0)],
  N.Participants = as.numeric(tabAge)[!(as.numeric(tabAge) == 0)],
  Context = rep(rownames(tabAge),times=3)[!(as.numeric(tabAge) == 0)])


ggplot(ggdf,aes(x=Gender,y=N.Participants,fill=Context)) + geom_bar(position="dodge",colour="white",stat="identity")  + labs(y="N participants") + scale_y_continuous(breaks=seq(0,90,10),limits=c(0,90)) + theme_bw() + ggtitle("Participants by gender")+  geom_text(aes(label = N.Participants), hjust=0.5, vjust=-0.25, size = 2.5,position=position_dodge(width=0.9)) 

```

```{r origns_by_context,message=FALSE}
# add numbers on the bar
tabAge <- t(table(all$origins,all$Context))
ggplot(all,aes(x=origins,fill=Context)) + geom_bar(position="dodge",colour="white") + ggtitle("Origins by context") + scale_y_continuous(breaks=seq(0,90,10),limits=c(0,90)) + theme_bw() + draw_grob(tableGrob(tabAge), x=2, y=60, width=0.3, height=0.4) + ggtitle("Participants by origins")
tabAge
```

- proficiency

```{r proficiency_by_context,message=FALSE}
tabAge <- t(table(all$prof,all$Context))
ggplot(all,aes(x=Context,fill=prof)) + geom_bar(position="dodge",colour="white") + ggtitle("Proficiency by context") + scale_y_continuous(breaks=seq(0,90,10),limits=c(0,90)) + theme_bw() + draw_grob(tableGrob(tabAge), x=2, y=80, width=0.3, height=0.4)
tabAge
```

- L2.VCE

```{r L2VCE_by_context,message=FALSE}
tabAge <- t(table(all[all$Context != "English in Germany" & all$Context != "English in Italy","L2.VCE"],all[all$Context != "English in Germany" & all$Context != "English in Italy",'Context'],useNA = "always"))
tabAge <- tabAge[-3,]

ggplot(all[all$Context != "English in Germany" & all$Context != "English in Italy",],aes(x=Context,fill=L2.VCE)) + geom_bar(position="dodge",colour="white") + ggtitle("L2.VCE by context") + scale_y_continuous(breaks=seq(0,90,10),limits=c(0,90)) + theme_bw() + draw_grob(tableGrob(tabAge), x=2, y=80, width=0.3, height=0.4)
```

- da mettere a posto con Richi

```{r year.studyL2_European_context,message=FALSE}
# year study L2
table(all$year.studyL2,all$other.year.studyL2.richi)

all$year.studyL2 <- ifelse(all$year.studyL2 == "Other",all$other.year.studyL2.richi,all$year.studyL2 )

# European context
ggplot(all[all$Context == "English in Germany" | all$Context == "English in Italy",],aes(x=degree,fill=year.studyL2)) + geom_bar(position="dodge",colour="white") + theme_bw() + ggtitle("Degree by study year L2, by Context") +  facet_grid(~Context,scales="free") + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + labs(y = "N participants", x = "degree")
```

- Degree of enrolment

```{r degree_by_context,message=FALSE}
# Australian context
tabAge <- t(table(all[all$Context == "Italian in Australia" | all$Context == "German in Australia",'degree'],all[all$Context == "Italian in Australia" | all$Context == "German in Australia",'Context']))
ggplot(all[all$Context == "Italian in Australia" | all$Context == "German in Australia",],aes(x=Context,fill=degree)) + geom_bar(position="dodge",colour="white") + theme_bw() + ggtitle("Degree in Australian Contexts") + draw_grob(tableGrob(tabAge), x=1., y=40, width=0.3, height=0.4)
tabAge
```

```{r year.studyL2_Australian_context,message=FALSE}
# Australian context
tabAge <- t(table(all[all$Context == "English in Italy" | all$Context == "English in Germany",'degree'],all[all$Context == "English in Italy" | all$Context == "English in Germany",'Context']))

ggplot(all[all$Context == "English in Italy" | all$Context == "English in Germany",],aes(x=Context,fill=degree)) + geom_bar(position="dodge",colour="white") + theme_bw() + ggtitle("Degree in European Contexts")

tabAge
```

\clearpage

# Likert scales

```{r include=FALSE,message=FALSE}
likert_grep <- "\\.id$|\\.ought$|\\.intr$|\\.instru$|\\.integr$|\\.prof$|\\.post$|\\.comm$|^necessity$|^educated$"

# all
likert_variables_all <- colnames(all)[grep(likert_grep,colnames(all))]
likert_variables_all
likert_variables_all <- likert_variables_all[!(likert_variables_all %in% "other.prof")]

```

- **Convert Likert scales to numbers**

```{r fig.width=15,fig.height=15}

convertToNumber <- function(column){
  column <- factor(column,levels = c("Strongly disagree","Disagree","Not sure","Agree","Strongly agree"))
  column_number <- as.numeric(column)
  return(column_number)
}

table(all$Context)

convert_likert <- data.frame(apply(subset(all,select=likert_variables_all),2,convertToNumber))
colnames(convert_likert) <- paste0(colnames(convert_likert),"1")

likert_variables1 <- paste0(likert_variables_all,"1")

# join the converted variables to the filtered dataset
filtered_conv <- cbind(all,convert_likert)

table(filtered_conv[,likert_variables_all[4]],filtered_conv[,likert_variables1[4]],useNA = "always")

write.csv(filtered_conv,"02-descriptive_data/merged_filtered_likertNumber.csv",row.names = FALSE)
```

## Impute missing values - Using median values

The missing values appears to be at random and there are max two missing values in one variable (see plots below). In order not to loose 12 participants while doing the factor analysis across contexts it is preferable to impute the 12 missing values. 

```{r}
all <- filtered_conv

# Items to use for factor analysis : items shared between contexts
# items to be used for the FA

usable_items <- likert_variables1[!(likert_variables1 %in% c("necessity1","educated1","reconnect.comm1", "speakersmelb.comm1", "comecloser.comm1"))]
```


```{r}
rownames(all) <- all$Resp.ID
usable_data_context <- all[,c(usable_items,"Context")]
dat_noNA <- usable_data_context[rowSums(is.na(usable_data_context)) == 0,]
all_noNA <- all[rowSums(is.na(usable_data_context)) == 0,]
table(rowSums(is.na(usable_data_context)))
# Participants with NA to remove
table(rowSums(is.na(usable_data_context)),usable_data_context$Context)

# check what to use to impute
# have a look at the distribution of missing values
library(mice)
library(VIM)

mice_plot <- aggr(usable_data_context[,usable_items], col=c('navyblue','yellow'),
                    numbers=TRUE, sortVars=TRUE,
                    labels=names(usable_data_context[,usable_items]), cex.axis=.4,
                    gap=1, ylab=c("Missing data","Pattern"),cex.numbers=0.5)

# Imputing using median
library(Hmisc)
imputedMedian <- usable_data_context

imputedMedian$globalaccess.post1 <- with(imputedMedian[,usable_items], impute(globalaccess.post1, median))
imputedMedian$citizen.post1 <- with(imputedMedian[,usable_items], impute(citizen.post1, median))
imputedMedian$money.instru1 <- with(imputedMedian[,usable_items], impute(money.instru1, median))
imputedMedian$knowledge.instru1 <- with(imputedMedian[,usable_items], impute(knowledge.instru1, median))
imputedMedian$life.intr1 <- with(imputedMedian[,usable_items], impute(life.intr1, median))
imputedMedian$time.integr1 <- with(imputedMedian[,usable_items], impute(time.integr1, median))
imputedMedian$expect.ought1 <- with(imputedMedian[,usable_items], impute(expect.ought1, median))
imputedMedian$job.instru1 <- with(imputedMedian[,usable_items], impute(job.instru1, median))
imputedMedian$career.instru1 <- with(imputedMedian[,usable_items], impute(career.instru1, median))
imputedMedian$meeting.integr1 <- with(imputedMedian[,usable_items], impute(meeting.integr1, median))
imputedMedian$interact.post1 <- with(imputedMedian[,usable_items], impute(interact.post1, median))


# check before after
table(imputedMedian$time.integr1)
table(usable_data_context$time.integr1)

table(imputedMedian$life.intr1)
table(usable_data_context$life.intr1)

table(imputedMedian$knowledge.instru1)
table(usable_data_context$knowledge.instru1)

table(imputedMedian$money.instru1)
table(usable_data_context$money.instru1)

table(imputedMedian$citizen.post1)
table(usable_data_context$citizen.post1)

table(imputedMedian$globalaccess.post1)
table(usable_data_context$globalaccess.post1)


table(imputedMedian$expect.ought1)
table(usable_data_context$expect.ought1)

table(imputedMedian$job.instru1)
table(usable_data_context$job.instru1)

table(imputedMedian$career.instru1)
table(usable_data_context$career.instru1)

table(imputedMedian$meeting.integr1)
table(usable_data_context$meeting.integr1)

table(imputedMedian$interact.post1)
table(usable_data_context$interact.post1)


```

- Substitute imputed data for the common variables to be used in the Factor Analysis

```{r}
all <- all[,!(colnames(all) %in% usable_items)]
imputedMedian$Context <- NULL
sum(!(colnames(imputedMedian) %in% usable_items))
all <- cbind(all,imputedMedian[match(rownames(imputedMedian),all$Resp.ID),])
```

## Save imputed data

```{r}
write.csv(all,"02-descriptive_data/merged_filtered_imputedMedian_likertNumber.csv",row.names = FALSE)
```

# Barplot of likert variables

```{r fig.width=20,fig.height=20}
all_melt <- melt(all,id.vars = c("Resp.ID","Gender","Age","prof","Context","study.year"),
                        measure.vars = likert_variables1)

all_melt$value <- factor(all_melt$value,levels=c(1,2,3,4,5),labels=c("Strongly disagree","Disagree","Not sure","Agree","Strongly agree"))
# dim(all_melt)
# 323*length(likert_variables1)

all_melt <- all_melt %>% separate(variable,into=c("item","type"),sep="\\.",remove=FALSE)
ggplot(all_melt,aes(x=variable,fill=value)) + geom_bar(position = "stack",colour="black") + 
  facet_grid(Context~type,scales = "free")+theme(axis.text.x = element_text(angle = 45, hjust = 1),axis.text=element_text(size=8)) + ggtitle("Filtered dataset") + scale_fill_manual(values=c("#ca0020","#f4a582","#ffffbf","#abd9e9","#2c7bb6","grey"))

filt_sum <- all_melt %>% group_by(Context,variable,type,value) %>% dplyr::summarise(Ngroup=length(value))
ggplot(filt_sum,aes(x=value,y=Ngroup,colour=Context,group=interaction(variable, Context))) + geom_line() + geom_point() + facet_wrap(~type,scales = "free")+theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

## Barplot of Educated and Necessity in the Australian and European Contexts

- **Educated**

```{r}
# add numbers on the bar
educated <- all[all$Context %in% c("German in Australia","Italian in Australia"),]
table(educated$educated1,educated$Context,useNA="always")
educated$educated1 <- factor(educated$educated1,levels = c(1,2,3,4,5),labels=c("Strongly disagree","Disagree","Not sure","Agree","Strongly agree")) 

tabEdu <- t(table(educated$educated1,educated$Context))
ggdf <- data.frame(Educated = rep(colnames(tabEdu),each=2),
  N.Participants = as.numeric(tabEdu),
  Context = rep(rownames(tabEdu),times=5))


ggplot(ggdf,aes(x=Educated,y=N.Participants,fill=Context)) + geom_bar(position="dodge",colour="white",stat="identity")  + labs(y="N participants") + scale_y_continuous(breaks=seq(0,35,10),limits=c(0,35)) + theme_bw() + ggtitle("Educated by Context")+  geom_text(aes(label = N.Participants), hjust=0.5, vjust=-0.25, size = 2.5,position=position_dodge(width=0.9)) 
ggplot(ggdf,aes(x=Context,y=N.Participants,fill=Educated)) + geom_bar(position="dodge",colour="white",stat="identity")  + labs(y="N participants") + scale_y_continuous(breaks=seq(0,35,10),limits=c(0,35)) + theme_bw() + ggtitle("Educated by Context")+  geom_text(aes(label = N.Participants), hjust=0.5, vjust=-0.25, size = 2.5,position=position_dodge(width=0.9)) 
```

- **Necessity**

```{r}
# add numbers on the bar
necessity <- all[all$Context %in% c("English in Germany","English in Italy"),]
table(necessity$necessity1,necessity$Context,useNA="always")
necessity$necessity1 <- factor(necessity$necessity1,levels = c(1,2,3,4,5),labels=c("Strongly disagree","Disagree","Not sure","Agree","Strongly agree")) 

tabNec <- t(table(necessity$necessity1,necessity$Context,useNA = "always"))[-3,]
ggdf <- data.frame(Necessity = rep(colnames(tabNec),each=2),
  N.Participants = as.numeric(tabNec),
  Context = rep(rownames(tabNec),times=6))


ggplot(ggdf,aes(x=Necessity,y=N.Participants,fill=Context)) + geom_bar(position="dodge",colour="white",stat="identity")  + labs(y="N participants") + scale_y_continuous(breaks=seq(0,40,10),limits=c(0,40)) + theme_bw() + ggtitle("Necessity by Context")+  geom_text(aes(label = N.Participants), hjust=0.5, vjust=-0.25, size = 2.5,position=position_dodge(width=0.9)) 
ggplot(ggdf,aes(x=Context,y=N.Participants,fill=Necessity)) + geom_bar(position="dodge",colour="white",stat="identity")  + labs(y="N participants") + scale_y_continuous(breaks=seq(0,35,10),limits=c(0,35)) + theme_bw() + ggtitle("Necessity by Context")+  geom_text(aes(label = N.Participants), hjust=0.5, vjust=-0.25, size = 2.5,position=position_dodge(width=0.9)) 
```

# Correlation plot of items by context

## Italian in Australia

```{r cor_italian_in_australia,fig.width=15,fig.height=15}
cov <- cor(filtered_conv[filtered_conv$Context == "Italian in Australia",likert_variables1[!(likert_variables1 %in% "necessity1")]],method = "pearson",use="pairwise.complete.obs")


row_infos <- data.frame(Variables=sapply(strsplit(colnames(cov),split="\\."),function(x) x[2]))
row_infos$Variables <- as.character(row_infos$Variables)
rownames(row_infos) <- rownames(cov)
row_infos$Variables[which(is.na(row_infos$Variables))] <- c("educated")
row_infos <- row_infos[order(row_infos$Variables),,drop=FALSE]

ann_col_wide <- data.frame(Variable=unique(row_infos$Variables))
ann_colors_wide <- list(Variables=c(comm1="#bd0026",educated="#b35806", id1="#f6e8c3",instru1="#35978f",integr1="#386cb0",intr1="#ffff99",ought1="grey",post1="black",prof1="pink"))

#pheatmap(cov, main = "Italian in Australia",annotation_names_row = FALSE,cluster_cols=TRUE,cluster_rows=TRUE,annotation_col = row_infos[,1,drop=FALSE], annotation_row = row_infos[,1,drop=FALSE],  annotation_colors = ann_colors_wide,breaks=seq(-1,1,0.2),col=c("#67001f","#b2182b","#d6604d","#f4a582","#fddbc7","#f7f7f7","#d1e5f0","#92c5de","#4393c3","#2166ac","#053061"),show_colnames = FALSE,width = 7,height = 7)
###################

diag(cov) <- NA
pheatmap(cov, main = "Italian in Australia",annotation_names_row = FALSE,cluster_cols=TRUE,cluster_rows=TRUE,annotation_col = row_infos[,1,drop=FALSE], annotation_row = row_infos[,1,drop=FALSE]
,  annotation_colors = ann_colors_wide,show_colnames = FALSE,breaks = seq(-0.6,0.7,length.out = 50),width = 7,height = 7,color=colorRampPalette(brewer.pal(n = 7, name = "RdBu"))(50))
```

## German in Australia

```{r cor_german_in_australia,fig.width=15,fig.height=15}
cov <- cor(filtered_conv[filtered_conv$Context == "German in Australia",likert_variables1[!(likert_variables1 %in% "necessity1")]],method = "pearson",use="pairwise.complete.obs")

row_infos <- data.frame(Variables=sapply(strsplit(colnames(cov),split="\\."),function(x) x[2]))
row_infos$Variables <- as.character(row_infos$Variables)
rownames(row_infos) <- rownames(cov)
row_infos$Variables[which(is.na(row_infos$Variables))] <- c("educated")
row_infos <- row_infos[order(row_infos$Variables),,drop=FALSE]

ann_col_wide <- data.frame(Variable=unique(row_infos$Variables))
ann_colors_wide <- list(Variables=c(comm1="#bd0026",educated="#b35806", id1="#f6e8c3",instru1="#35978f",integr1="#386cb0",intr1="#ffff99",ought1="grey",post1="black",prof1="pink"))

diag(cov) <- NA
pheatmap(cov, main = "German in Australia",annotation_names_row = FALSE,cluster_cols=TRUE,cluster_rows=TRUE,annotation_col = row_infos[,1,drop=FALSE], annotation_row = row_infos[,1,drop=FALSE]
,  annotation_colors = ann_colors_wide,show_colnames = FALSE,breaks = seq(-0.6,0.7,length.out = 50),width = 7,height = 7,color=colorRampPalette(brewer.pal(n = 7, name = "RdBu"))(50))
```

## English in Germany

```{r cor_english_in_germany,fig.width=15,fig.height=15}
cov <- cor(filtered_conv[filtered_conv$Context == "English in Germany",likert_variables1[!(likert_variables1 %in% c("reconnect.comm1",    "speakersmelb.comm1","comecloser.comm1","educated1"))]],method = "pearson",use="pairwise.complete.obs")

row_infos <- data.frame(Variables=sapply(strsplit(colnames(cov),split="\\."),function(x) x[2]))
row_infos$Variables <- as.character(row_infos$Variables)
rownames(row_infos) <- rownames(cov)
row_infos$Variables[which(is.na(row_infos$Variables))] <- c("necessity")
row_infos <- row_infos[order(row_infos$Variables),,drop=FALSE]

ann_col_wide <- data.frame(Variable=unique(row_infos$Variables))
ann_colors_wide <- list(Variables=c(id1="#f6e8c3",necessity="#b35806",instru1="#35978f",integr1="#386cb0",intr1="#ffff99",ought1="grey",post1="black",prof1="pink"))

diag(cov) <- NA
pheatmap(cov, main = "English in Germany",annotation_names_row = FALSE,cluster_cols=TRUE,cluster_rows=TRUE,annotation_col = row_infos[,1,drop=FALSE], annotation_row = row_infos[,1,drop=FALSE]
,  annotation_colors = ann_colors_wide,show_colnames = FALSE,breaks = seq(-0.6,0.7,length.out = 50),width = 7,height = 7,color=colorRampPalette(brewer.pal(n = 7, name = "RdBu"))(50))
```

## English in Italy

```{r cor_english_in_italy,fig.width=15,fig.height=15}
cov <- cor(filtered_conv[filtered_conv$Context == "English in Italy",likert_variables1[!(likert_variables1 %in% c("reconnect.comm1","speakersmelb.comm1","comecloser.comm1","educated1"))]],method = "pearson",use="pairwise.complete.obs")

row_infos <- data.frame(Variables=sapply(strsplit(colnames(cov),split="\\."),function(x) x[2]))
row_infos$Variables <- as.character(row_infos$Variables)
rownames(row_infos) <- rownames(cov)
row_infos$Variables[which(is.na(row_infos$Variables))] <- "necessity"
row_infos <- row_infos[order(row_infos$Variables),,drop=FALSE]

ann_col_wide <- data.frame(Variable=unique(row_infos$Variables))
ann_colors_wide <- list(Variables=c(comm1="#bd0026",necessity="#b35806", id1="#f6e8c3",instru1="#35978f",integr1="#386cb0",intr1="#ffff99",ought1="grey",post1="black",prof1="pink"))

diag(cov) <- NA
pheatmap(cov, main = "English in Italy",annotation_names_row = FALSE,cluster_cols=TRUE,cluster_rows=TRUE,annotation_col = row_infos[,1,drop=FALSE], annotation_row = row_infos[,1,drop=FALSE]
,  annotation_colors = ann_colors_wide,show_colnames = FALSE,breaks = seq(-0.6,0.7,length.out = 50),width = 7,height = 7,color=colorRampPalette(brewer.pal(n = 7, name = "RdBu"))(50))
```

## All context together

```{r cor_all_contexts}
cov <- cor(filtered_conv[,likert_variables1],method = "pearson",use="pairwise.complete.obs")

row_infos <- data.frame(Variables=sapply(strsplit(colnames(cov),split="\\."),function(x) x[2]))
row_infos$Variables <- as.character(row_infos$Variables)
rownames(row_infos) <- rownames(cov)
row_infos$Variables[which(is.na(row_infos$Variables))] <- c("necessity","educated")
row_infos <- row_infos[order(row_infos$Variables),,drop=FALSE]

ann_col_wide <- data.frame(Variable=unique(row_infos$Variables))
ann_colors_wide <- list(Variables=c(comm1="#bd0026",educated="orange", id1="#f6e8c3",instru1="#35978f",necessity="#b35806",integr1="#386cb0",intr1="#ffff99",ought1="grey",post1="black",prof1="pink"))

diag(cov) <- NA
pheatmap(cov, main = "All Contexts",annotation_names_row = FALSE,cluster_cols=TRUE,cluster_rows=TRUE,annotation_col = row_infos[,1,drop=FALSE], annotation_row = row_infos[,1,drop=FALSE]
,  annotation_colors = ann_colors_wide,show_colnames = FALSE,breaks = seq(-0.6,0.7,length.out = 50),width = 7,height = 7,color=colorRampPalette(brewer.pal(n = 7, name = "RdBu"))(50))

```

# Evaluate internal consistency of known constructs with alpha

```{r}
sets <- list(id.var=likert_variables1[grep("\\.id1$",likert_variables1)],
             ought.var=likert_variables1[grep("\\.ought1$",likert_variables1)],
             intr.var=likert_variables1[grep("\\.intr1$",likert_variables1)],
             instru.var=likert_variables1[grep("\\.instru1$",likert_variables1)],
             integr1.var=likert_variables1[grep("\\.integr1$",likert_variables1)],
             prof.var=likert_variables1[grep("\\.prof1$",likert_variables1)],
             post.var=likert_variables1[grep("\\.post1$",likert_variables1)],
             comm.var=likert_variables1[grep("\\.comm1$",likert_variables1)])
              

get_alpha <- function(dataMot,
                      var=sets$id.var){
  var_alpha <- alpha(dataMot[,var])
  dataf <- data.frame(alpha=var_alpha$total,
                    drop = var_alpha$alpha.drop)
  rownames(dataf) <- rownames(var_alpha$alpha.drop)
  return(dataf)
}

# "Italian in Australia"
ita_in_au <- do.call(rbind,lapply(sets,function(x) {
  get_alpha(data=filtered_conv[filtered_conv$Context == "Italian in Australia",],
                      var=x)}))
ita_in_au$var <- sapply(strsplit(rownames(ita_in_au),split="\\."),function(x) x[1]) 
ita_in_au$var.full <- sapply(strsplit(rownames(ita_in_au),split="\\."),function(x) x[3]) 
ita_in_au$Context <- "Italian in Australia"
rownames(ita_in_au) <- NULL

# "German in Australia"
germ_in_au <- do.call(rbind,lapply(sets,function(x) {
  get_alpha(data=filtered_conv[filtered_conv$Context == "German in Australia",],
                      var=x)}))
germ_in_au$var <- sapply(strsplit(rownames(germ_in_au),split="\\."),function(x) x[1]) 
germ_in_au$var.full <- sapply(strsplit(rownames(germ_in_au),split="\\."),function(x) x[3]) 
germ_in_au$Context <- "German in Australia"
rownames(germ_in_au) <- NULL

# "English in Germany"
eng_in_germ <- do.call(rbind,lapply(sets[!(names(sets) %in% "comm.var")],function(x) {
  get_alpha(data=filtered_conv[filtered_conv$Context == "English in Germany",],
                      var=x)}))

# the ones that makes issues
get_alpha(data=filtered_conv[filtered_conv$Context == "English in Germany",],
                      var=sets$ought.var)

eng_in_germ$var <- sapply(strsplit(rownames(eng_in_germ),split="\\."),function(x) x[1]) 
eng_in_germ$var.full <- sapply(strsplit(rownames(eng_in_germ),split="\\."),function(x) x[3]) 
eng_in_germ$Context <- "English in Germany"
rownames(eng_in_germ) <- NULL

# "English in Italy"
eng_in_ita <- do.call(rbind,lapply(sets[!(names(sets) %in% "comm.var")],function(x) {
  get_alpha(data=filtered_conv[filtered_conv$Context == "English in Italy",],
                      var=x)}))
eng_in_ita$var <- sapply(strsplit(rownames(eng_in_ita),split="\\."),function(x) x[1]) 
eng_in_ita$var.full <- sapply(strsplit(rownames(eng_in_ita),split="\\."),function(x) x[3]) 
eng_in_ita$Context <- "English in Italy"
rownames(eng_in_ita) <- NULL


# combine
full_alpha <- rbind(eng_in_ita,eng_in_germ,germ_in_au,ita_in_au)

```

- Plot alpha by variable

```{r alpha_chronbach_by_context}

full_alpha %>% group_by(Context,var) %>% 
  summarise(st.alpha = unique(alpha.std.alpha),
            G6=unique(alpha.G6.smc.)) %>%
  ggplot(.,aes(x=var,y=st.alpha,colour=Context)) + geom_point() + geom_line(aes(group=Context)) + theme_bw()

```


```{r fig.height=18,fig.width=14}
all_melt <- all_melt %>% separate(variable,into=c("item","type"),sep="\\.",remove=FALSE)
p1=ggplot(all_melt,aes(x=variable,fill=value)) + geom_bar(position = "stack") + 
  facet_grid(Context~type,scales = "free") + ggtitle("Filtered dataset")+theme(axis.text.x = element_text(angle = 45, hjust = 1),axis.text=element_text(size=8))+theme_bw()

p2=ggplot(full_alpha,aes(x=var.full,y=drop.std.alpha,colour=Context)) + geom_point() + geom_line(aes(group=Context)) + theme_bw() + facet_wrap(~var,scales="free")

p4=ggplot(full_alpha,aes(x=var.full,y=drop.average_r,colour=Context)) + geom_point() + geom_line(aes(group=Context)) + theme_bw() + facet_wrap(~var,scales="free")

p3=full_alpha %>% group_by(Context,var) %>% 
  summarise(st.alpha = unique(alpha.std.alpha),
            G6=unique(alpha.G6.smc.)) %>%
  ggplot(.,aes(x=var,y=st.alpha,colour=Context)) + geom_point() + geom_line(aes(group=Context)) + theme(axis.text.x = element_text(angle = 45, hjust = 1),axis.text=element_text(size=8)) + theme_bw()


cowplot::plot_grid(p2,p3,nrow=2)

```

