---
title: "Analysis of merged questionnaires"
author: "Anna Quaglieri & Riccardo Amorati"
date: "03/09/2017"
output:
  html_document: default
  pdf_document: default
---


```{r,message=FALSE}
library(readr)
library(tidyverse)
library(reshape2)
library(corrplot)
library(psych)
library(pheatmap)
library(RColorBrewer)
library(cowplot)
# Chunk options
knitr::opts_chunk$set(echo = TRUE, prompt = TRUE,cache = TRUE)

```

# Read in data

```{r message=FALSE,message=FALSE}
european <- read_csv("european_recoded.csv")
australian <- read_csv("australian_recoded.csv")

all <- merge(european,australian,all = TRUE)
```

## Variables that are interesting but are different between contexts

```{r}
demographics_var <- c("Age","Gender","L1","speak.other.L2","study.other.L2","origins","year.studyL2","other5.other.ways","degree","roleL2.degree","study.year","prof","L2.VCE","uni1.year","Context")
l2School <- "\\.L2school$"
l2School_variables <- colnames(all)[grep(l2School,colnames(all))]
```

- First language

```{r}
#table(all$L1,all$Context) # too many levels - needs to be cleaned (ex tot number of languages?)
table(all$L1,useNA = "always")
ggplot(all,aes(x=L1,fill=Context)) + geom_bar() + coord_flip() + ggtitle("First Language") + labs(y="N. of participants",x="")
#table(all$speak.other.L2,all$Context)
```

```{r}
L2 <- data.frame(Freq=table(all$speak.other.L2)[order(table(all$speak.other.L2),decreasing = TRUE)],
                 L2=names(table(all$speak.other.L2))[order(table(all$speak.other.L2),decreasing = TRUE)]) # too many levels - needs to be cleaned (ex tot number of languages?)
head(L2)
```

- origins

```{r}
table(all$origins,useNA = "always")
```


```{r}
table(all$year.studyL2)
```

```{r}
table(all$degree)
```

- study.year in the European context is uni1.year in the Australian context

```{r}
all$study.year[is.na(all$study.year)] <- all$uni1.year[is.na(all$study.year)]
#table(all$study.year)
all$study.year <- ifelse(all$study.year == "Already graduated after 5 semesters in March 2016, was interested in survery/study, sorry.","6th semester",all$study.year)
table(all$study.year)
```

- proficiency

```{r}
table(all$prof,useNA = "always")
```

- Barplot filtered

```{r include=FALSE,message=FALSE}
likert_grep <- "\\.id$|\\.ought$|\\.intr$|\\.instru$|\\.integr$|\\.prof$|\\.post$|\\.comm$|^necessity$|^educated$"

# all
likert_variables_all <- colnames(all)[grep(likert_grep,colnames(all))]
likert_variables_all
likert_variables_all <- likert_variables_all[!(likert_variables_all %in% "other.prof")]
```

# Filter participants : keep only the ones that meet the inclusion criteria.

```{r Filtered,fig.width=20,fig.height=15}
all$study.year[is.na(all$study.year)] <- all$uni1.year[is.na(all$study.year)]
# Filter only subject that we want to include in the study
# names(table(all$study.year))[1] = 1st semester"

filtered <- subset(all, (study.year == "1st year") | (study.year == names(table(all$study.year))[1]) & year.studyL2 != "0 years")

table(filtered$Context)
table(all$Context)
```

## Demographics

```{r message=FALSE}
all <- filtered
demographics_var <- c("Age","Gender","L1","speak.other.L2","study.other.L2","origins","year.studyL2","other5.other.ways","degree","roleL2.degree","study.year","prof","L2.VCE","uni1.year","Context")
l2School <- "\\.L2school$"
l2School_variables <- colnames(all)[grep(l2School,colnames(all))]

ggplot(all,aes(x=L1,fill=Context)) + geom_bar() + coord_flip() + ggtitle("First Language") + labs(y="N. of participants",x="") + theme_bw()

table(all$L1,all$Context)

```

- Filter for L1

```{r}
#Filter by L1

nc <- names(table(all$Context))
l1_filter <- all[(all$Context == nc[1] & (all$L1 == "German" | all$L1 == "German and English")) | 
                    (all$Context == nc[2] & (all$L1 == "Italian")) | 
                    (all$Context == nc[3] & (all$L1 == "English" | all$L1 == "English and Dutch" | all$L1 == "German and English")) |
                    (all$Context == nc[4] & (all$L1 == "English" | all$L1 == "English and Dutch" | all$L1 == "German and English")),]


all <- l1_filter

# subset demographics
demo <- subset(all,select=c("Resp.ID",demographics_var,l2School_variables))

# Numeri finali
table(l1_filter$Context)

```

- Filter missing value:
  - Filter participants who didn't put the degree
  - we don't care about speak.other.L2 and study.other.L2

```{r}
missing_bySample <- rowSums(is.na(demo))
names(missing_bySample) <- demo$Resp.ID
missing_byVar <- colSums(is.na(demo))
names(missing_byVar) <- colnames(demo)

barplot(missing_bySample)
d <- data.frame(miss=missing_byVar)
d$varID <- rownames(d)
ggplot(data=d,aes(x=varID,y=miss)) + geom_bar(stat="identity") + theme_bw() +theme(axis.text.x = element_text(angle = 45, hjust = 1)) 


demo_missing <- demo %>% group_by(Context) %>% summarise(roleL2.degree_na = sum(is.na(roleL2.degree)),
                                                         L2.VCE_na = sum(is.na(L2.VCE)),
                                                         other5.other.ways_na=sum(is.na(other5.other.ways )),
                                                         uni1.year_na = sum(is.na(uni1.year)),
                                                         primary1.L2school_na=sum(is.na(primary1.L2school)),
                                                         CLS3.L2school_na = sum(is.na(CLS3.L2school)),
                                                         VSL4.L2school_na=sum(is.na(VSL4.L2school)),
                                                         degree = sum(is.na(degree)),
                                                         schooL2country5.L2school_na=sum(is.na(schooL2country5.L2school)))

# We do not filter for speak.other.L2 or study.other.L2

#demo[is.na(demo$speak.other.L2),]
# teniamo
#demo[is.na(demo$study.other.L2),]
missing_bySample[names(missing_bySample) == "5166861581"]
#demo[is.na(demo$year.studyL2),]
missing_bySample[names(missing_bySample) == "5378798787"]

# remove NA from degree
#table(demo$degree,useNA = "always")
# Remove people
all <- all[!is.na(all$degree),]


table(all$Context)
```

- Summary demographics

  - to change yearL2.study.richi 

```{r message=FALSE}
# add numbers on the bar
ggplot(all,aes(x=Age,fill=Context)) + geom_bar(position="dodge",colour="white")  + theme_bw() + labs(y="N participants")
# add numbers on the bar
ggplot(all,aes(x=origins,fill=Context)) + geom_bar(position="dodge",colour="white") + theme_bw() + ggtitle("Origins by context")

# year study L2
table(all$year.studyL2,all$other.year.studyL2.richi)
all$year.studyL2 <- ifelse(all$year.studyL2 == "Other",all$other.year.studyL2.richi,all$year.studyL2 )

# European context
ggplot(all[all$Context == "English in Germany" | all$Context == "English in Italy",],aes(x=degree,fill=year.studyL2)) + geom_bar(position="dodge",colour="white") + theme_bw() + ggtitle("Degree by study year L2, by Context") +  facet_grid(~Context,scales="free") + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + labs(y = "N participants", x = "degree")

# Australian context
ggplot(all[all$Context == "Italian in Australia" | all$Context == "German in Australia",],aes(x=degree,fill=study.year)) + geom_bar(position="dodge",colour="white") + theme_bw() + ggtitle("Degree by study year, by previous study") + coord_flip() + facet_grid(Context~year.studyL2,scales="free")

```


```{r fig.width=20,fig.height=15}
all_melt <- melt(all,id.vars = c("Resp.ID","Gender","Age","prof","Context","study.year"),
                        measure.vars = likert_variables_all)

all_melt$value <- factor(all_melt$value,levels=c("Strongly disagree","Disagree","Not sure","Agree","Strongly agree"))

all_melt <- all_melt %>% separate(variable,into=c("item","type"),sep="\\.",remove=FALSE)
ggplot(all_melt,aes(x=variable,fill=value)) + geom_bar(position = "stack") + 
  facet_grid(Context~type,scales = "free")+theme(axis.text.x = element_text(angle = 45, hjust = 1),axis.text=element_text(size=8)) + ggtitle("Filtered dataset")

filt_sum <- all_melt %>% group_by(Context,variable,type,value) %>% dplyr::summarise(Ngroup=length(value))
ggplot(filt_sum,aes(x=value,y=Ngroup,colour=Context,group=interaction(variable, Context))) + geom_line() + geom_point() + facet_wrap(~type,scales = "free")+theme(axis.text.x = element_text(angle = 45, hjust = 1))

```


# Convert Likert scales to numbers

- correlation plot of items by context

```{r fig.width=15,fig.height=15}
convertToNumber <- function(column){
  column <- factor(column,levels = c("Strongly disagree","Disagree","Not sure","Agree","Strongly agree"))
  column_number <- as.numeric(column)
  return(column_number)
}

table(all$Context)

convert_likert <- data.frame(apply(subset(all,select=likert_variables_all),2,convertToNumber))
colnames(convert_likert) <- paste0(colnames(convert_likert),"1")

likert_variables1 <- paste0(likert_variables_all,"1")

# join the converted variables to the filtered dataset
filtered_conv <- cbind(all,convert_likert)

table(filtered_conv[,likert_variables_all[1]],filtered_conv[,likert_variables1[1]],useNA = "always")
```

- Italian in Australia

```{r fig.width=15,fig.height=15}
cov <- cor(filtered_conv[filtered_conv$Context == "Italian in Australia",likert_variables1[!(likert_variables1 %in% "necessity1")]],method = "pearson",use="pairwise.complete.obs")
#corrplot(cov,method="color",is.corr = TRUE,order = "hclust",tl.col = "black",mar = c(1, 0,1, 0),tl.cex=0.8)

library(pheatmap)
row_infos <- data.frame(Variables=sapply(strsplit(colnames(cov),split="\\."),function(x) x[2]))
row_infos$Variables <- as.character(row_infos$Variables)
rownames(row_infos) <- rownames(cov)
row_infos$Variables[which(is.na(row_infos$Variables))] <- c("educated")
row_infos <- row_infos[order(row_infos$Variables),,drop=FALSE]

ann_col_wide <- data.frame(Variable=unique(row_infos$Variables))
ann_colors_wide <- list(Variables=c(comm1="#bd0026",educated="#b35806", id1="#f6e8c3",instru1="#35978f",integr1="#386cb0",intr1="#ffff99",ought1="grey",post1="black",prof1="pink"))

#pheatmap(cov, main = "Italian in Australia",annotation_names_row = FALSE,cluster_cols=TRUE,cluster_rows=TRUE,annotation_col = row_infos[,1,drop=FALSE], annotation_row = row_infos[,1,drop=FALSE],  annotation_colors = ann_colors_wide,breaks=seq(-1,1,0.2),col=c("#67001f","#b2182b","#d6604d","#f4a582","#fddbc7","#f7f7f7","#d1e5f0","#92c5de","#4393c3","#2166ac","#053061"),show_colnames = FALSE,width = 7,height = 7)
###################

diag(cov) <- NA
pheatmap(cov, main = "Italian in Australia",annotation_names_row = FALSE,cluster_cols=TRUE,cluster_rows=TRUE,annotation_col = row_infos[,1,drop=FALSE], annotation_row = row_infos[,1,drop=FALSE]
,  annotation_colors = ann_colors_wide,show_colnames = FALSE,breaks = seq(-0.6,0.7,length.out = 50),width = 7,height = 7,color=colorRampPalette(brewer.pal(n = 7, name = "RdBu"))(50))
```

- German in Australia

```{r fig.width=15,fig.height=15}
cov <- cor(filtered_conv[filtered_conv$Context == "German in Australia",likert_variables1[!(likert_variables1 %in% "necessity1")]],method = "pearson",use="pairwise.complete.obs")

row_infos <- data.frame(Variables=sapply(strsplit(colnames(cov),split="\\."),function(x) x[2]))
row_infos$Variables <- as.character(row_infos$Variables)
rownames(row_infos) <- rownames(cov)
row_infos$Variables[which(is.na(row_infos$Variables))] <- c("educated")
row_infos <- row_infos[order(row_infos$Variables),,drop=FALSE]

ann_col_wide <- data.frame(Variable=unique(row_infos$Variables))
ann_colors_wide <- list(Variables=c(comm1="#bd0026",educated="#b35806", id1="#f6e8c3",instru1="#35978f",integr1="#386cb0",intr1="#ffff99",ought1="grey",post1="black",prof1="pink"))

diag(cov) <- NA
pheatmap(cov, main = "German in Australia",annotation_names_row = FALSE,cluster_cols=TRUE,cluster_rows=TRUE,annotation_col = row_infos[,1,drop=FALSE], annotation_row = row_infos[,1,drop=FALSE]
,  annotation_colors = ann_colors_wide,show_colnames = FALSE,breaks = seq(-0.6,0.7,length.out = 50),width = 7,height = 7,color=colorRampPalette(brewer.pal(n = 7, name = "RdBu"))(50))
```

- English in Germany

```{r fig.width=15,fig.height=15}
cov <- cor(filtered_conv[filtered_conv$Context == "English in Germany",likert_variables1[!(likert_variables1 %in% c("reconnect.comm1",    "speakersmelb.comm1","comecloser.comm1","educated1"))]],method = "pearson",use="pairwise.complete.obs")

row_infos <- data.frame(Variables=sapply(strsplit(colnames(cov),split="\\."),function(x) x[2]))
row_infos$Variables <- as.character(row_infos$Variables)
rownames(row_infos) <- rownames(cov)
row_infos$Variables[which(is.na(row_infos$Variables))] <- c("necessity")
row_infos <- row_infos[order(row_infos$Variables),,drop=FALSE]

ann_col_wide <- data.frame(Variable=unique(row_infos$Variables))
ann_colors_wide <- list(Variables=c(id1="#f6e8c3",necessity="#b35806",instru1="#35978f",integr1="#386cb0",intr1="#ffff99",ought1="grey",post1="black",prof1="pink"))

diag(cov) <- NA
pheatmap(cov, main = "English in Germany",annotation_names_row = FALSE,cluster_cols=TRUE,cluster_rows=TRUE,annotation_col = row_infos[,1,drop=FALSE], annotation_row = row_infos[,1,drop=FALSE]
,  annotation_colors = ann_colors_wide,show_colnames = FALSE,breaks = seq(-0.6,0.7,length.out = 50),width = 7,height = 7,color=colorRampPalette(brewer.pal(n = 7, name = "RdBu"))(50))
```

- English in Italy

```{r fig.width=15,fig.height=15}
cov <- cor(filtered_conv[filtered_conv$Context == "English in Italy",likert_variables1[!(likert_variables1 %in% c("reconnect.comm1","speakersmelb.comm1","comecloser.comm1","educated1"))]],method = "pearson",use="pairwise.complete.obs")

row_infos <- data.frame(Variables=sapply(strsplit(colnames(cov),split="\\."),function(x) x[2]))
row_infos$Variables <- as.character(row_infos$Variables)
rownames(row_infos) <- rownames(cov)
row_infos$Variables[which(is.na(row_infos$Variables))] <- "necessity"
row_infos <- row_infos[order(row_infos$Variables),,drop=FALSE]

ann_col_wide <- data.frame(Variable=unique(row_infos$Variables))
ann_colors_wide <- list(Variables=c(comm1="#bd0026",necessity="#b35806", id1="#f6e8c3",instru1="#35978f",integr1="#386cb0",intr1="#ffff99",ought1="grey",post1="black",prof1="pink"))

diag(cov) <- NA
pheatmap(cov, main = "English in Italy",annotation_names_row = FALSE,cluster_cols=TRUE,cluster_rows=TRUE,annotation_col = row_infos[,1,drop=FALSE], annotation_row = row_infos[,1,drop=FALSE]
,  annotation_colors = ann_colors_wide,show_colnames = FALSE,breaks = seq(-0.6,0.7,length.out = 50),width = 7,height = 7,color=colorRampPalette(brewer.pal(n = 7, name = "RdBu"))(50))
```


```{r}
cov <- cor(filtered_conv[,likert_variables1],method = "pearson",use="pairwise.complete.obs")

row_infos <- data.frame(Variables=sapply(strsplit(colnames(cov),split="\\."),function(x) x[2]))
row_infos$Variables <- as.character(row_infos$Variables)
rownames(row_infos) <- rownames(cov)
row_infos$Variables[which(is.na(row_infos$Variables))] <- c("necessity","educated")
row_infos <- row_infos[order(row_infos$Variables),,drop=FALSE]

ann_col_wide <- data.frame(Variable=unique(row_infos$Variables))
ann_colors_wide <- list(Variables=c(comm1="#bd0026",educated="orange", id1="#f6e8c3",instru1="#35978f",necessity="#b35806",integr1="#386cb0",intr1="#ffff99",ought1="grey",post1="black",prof1="pink"))

diag(cov) <- NA
pheatmap(cov, main = "All Contexts",annotation_names_row = FALSE,cluster_cols=TRUE,cluster_rows=TRUE,annotation_col = row_infos[,1,drop=FALSE], annotation_row = row_infos[,1,drop=FALSE]
,  annotation_colors = ann_colors_wide,show_colnames = FALSE,breaks = seq(-0.6,0.7,length.out = 50),width = 7,height = 7,color=colorRampPalette(brewer.pal(n = 7, name = "RdBu"))(50))

```


## Evaluate internal constiency of known constructs

```{r}
sets <- list(id.var=likert_variables1[grep("\\.id1$",likert_variables1)],
             ought.var=likert_variables1[grep("\\.ought1$",likert_variables1)],
             intr.var=likert_variables1[grep("\\.intr1$",likert_variables1)],
             instru.var=likert_variables1[grep("\\.instru1$",likert_variables1)],
             integr1.var=likert_variables1[grep("\\.integr1$",likert_variables1)],
             prof.var=likert_variables1[grep("\\.prof1$",likert_variables1)],
             post.var=likert_variables1[grep("\\.post1$",likert_variables1)],
             comm.var=likert_variables1[grep("\\.comm1$",likert_variables1)])
              

get_alpha <- function(data=filtered_conv[filtered$Context == "Italian in Australia",],
                      var=sets$id.var){
  var_alpha <- alpha(data[,var])
  dataf <- data.frame(alpha=var_alpha$total,
                    drop = var_alpha$alpha.drop)
  rownames(dataf) <- rownames(var_alpha$alpha.drop)
  return(dataf)
}

# "Italian in Australia"
ita_in_au <- do.call(rbind,lapply(sets,function(x) {
  get_alpha(data=filtered_conv[filtered$Context == "Italian in Australia",],
                      var=x)}))
ita_in_au$var <- sapply(strsplit(rownames(ita_in_au),split="\\."),function(x) x[1]) 
ita_in_au$var.full <- sapply(strsplit(rownames(ita_in_au),split="\\."),function(x) x[3]) 
ita_in_au$Context <- "Italian in Australia"
rownames(ita_in_au) <- NULL

# "German in Australia"
germ_in_au <- do.call(rbind,lapply(sets,function(x) {
  get_alpha(data=filtered_conv[filtered$Context == "German in Australia",],
                      var=x)}))
germ_in_au$var <- sapply(strsplit(rownames(germ_in_au),split="\\."),function(x) x[1]) 
germ_in_au$var.full <- sapply(strsplit(rownames(germ_in_au),split="\\."),function(x) x[3]) 
germ_in_au$Context <- "German in Australia"
rownames(germ_in_au) <- NULL

# "English in Germany"
eng_in_germ <- do.call(rbind,lapply(sets[!(names(sets) %in% "comm.var")],function(x) {
  get_alpha(data=filtered_conv[filtered$Context == "English in Germany",],
                      var=x)}))

# the ones that makes issues
get_alpha(data=filtered_conv[filtered$Context == "English in Germany",],
                      var=sets$ought.var)

eng_in_germ$var <- sapply(strsplit(rownames(eng_in_germ),split="\\."),function(x) x[1]) 
eng_in_germ$var.full <- sapply(strsplit(rownames(eng_in_germ),split="\\."),function(x) x[3]) 
eng_in_germ$Context <- "English in Germany"
rownames(eng_in_germ) <- NULL

# "English in Italy"
eng_in_ita <- do.call(rbind,lapply(sets[!(names(sets) %in% "comm.var")],function(x) {
  get_alpha(data=filtered_conv[filtered$Context == "English in Italy",],
                      var=x)}))
eng_in_ita$var <- sapply(strsplit(rownames(eng_in_ita),split="\\."),function(x) x[1]) 
eng_in_ita$var.full <- sapply(strsplit(rownames(eng_in_ita),split="\\."),function(x) x[3]) 
eng_in_ita$Context <- "English in Italy"
rownames(eng_in_ita) <- NULL

# combine
full_alpha <- rbind(eng_in_ita,eng_in_germ,germ_in_au,ita_in_au)

```

- Plot alpha by variable

```{r}

full_alpha %>% group_by(Context,var) %>% 
  summarise(st.alpha = unique(alpha.std.alpha),
            G6=unique(alpha.G6.smc.)) %>%
  ggplot(.,aes(x=var,y=st.alpha,colour=Context)) + geom_point() + geom_line(aes(group=Context)) + theme_bw()

```


```{r fig.height=18,fig.width=14}
all_melt <- all_melt %>% separate(variable,into=c("item","type"),sep="\\.",remove=FALSE)
p1=ggplot(all_melt,aes(x=variable,fill=value)) + geom_bar(position = "stack") + 
  facet_grid(Context~type,scales = "free") + ggtitle("Filtered dataset")+theme(axis.text.x = element_text(angle = 45, hjust = 1),axis.text=element_text(size=8))

p2=ggplot(full_alpha,aes(x=var.full,y=drop.std.alpha,colour=Context)) + geom_point() + geom_line(aes(group=Context)) + theme_bw() + facet_wrap(~var,scales="free")

p4=ggplot(full_alpha,aes(x=var.full,y=drop.average_r,colour=Context)) + geom_point() + geom_line(aes(group=Context)) + theme_bw() + facet_wrap(~var,scales="free")

p3=full_alpha %>% group_by(Context,var) %>% 
  summarise(st.alpha = unique(alpha.std.alpha),
            G6=unique(alpha.G6.smc.)) %>%
  ggplot(.,aes(x=var,y=st.alpha,colour=Context)) + geom_point() + geom_line(aes(group=Context)) + theme(axis.text.x = element_text(angle = 45, hjust = 1),axis.text=element_text(size=8))


plot_grid(p2,p3,p1,p4,nrow=4)

```